Proportional multi-state multiple-cohort life table model

### 2018-04-18 MSLT/MSLTdoc.Rmd
loop spline

##Loop to generate interpolated values for all cause mortality and all-cause years lived with disability.

@@

    data <- filter(GBDGL, measure == "ylds (years lived with disability)", sex == "female", cause == "all       causes") %>% select(measure, location, sex, age, metric, cause, val, age_cat, one_rate)
    assign(paste(i_sex, i_measure, "interpolated_data", sep = " "), data)
x=data$age_cat
y=log(data$one_rate)

>>>>

@@

    data <- filter(GBDGL, measure == i_measure, sex == i_sex, cause == "all causes") %>% select(measure, location, sex, age, metric, cause, val, age_cat, one_rate) 
    assign(paste(i_sex, i_measure, "interpolated_data", sep = " "), data)
x=data$age_cat
y=log(data$one_rate)
